BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-09 Paper/D5.5/D5.5.tex
More deliverable.

Running existing applications on those new architectures is an open project.
Thus, those projects have work packages dedicated to applications. Those
workpackages are dedicated to porting and optimizing Scientific applications on
those new architectures. In the DEEP project six applications were selected for
porting and optimizing, eleven were selected in the Mont-Blanc project.

@@

Developed by physicist, chemist, meteorologist. Usually in FORTRAN for
historical and performance reason. Codes can be quite huge (several
thousands lines of code) with lots of functionalities. Nonetheless they are
usually based on computing kernels. Computing kernels are resource
intensive and well defined parts of a program with a limited set of input
and output. Those kernels are the time consuming part of an HPC
application. They are thus the prime target for optimization.

@@

>>>>

@@

Scientific Computing Applications are usually developed by physicist, chemist or
meteorologist. Usually in FORTRAN for historical and performance reason. Codes
can be quite huge (several thousands lines of code) with lots of
functionalities. Nonetheless they are usually based on computing kernels.
Computing kernels are resource intensive and well defined parts of a program
with a limited set of input and output. Those kernels are the time consuming
part of an HPC application. They are thus the prime target for optimization.

@@

Running existing applications on those new architectures is an open project.
Thus, those projects have work packages dedicated to applications. Those
work packages are dedicated to porting and optimizing Scientific applications on
those new architectures. In the DEEP project six applications were selected for
porting and optimizing, eleven were selected in the Mont-Blanc project.

\section{Motivating Example}
